Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-11-14 awipev-CO2.Rmd
server text updated

- (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
00 01 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R

- (At 03:00, web page is generated)
00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1

- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud/Exp168)
00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

- (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

>>>>

- (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)

00 01 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R

- (At 03:00, web page is generated)

00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1

- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud/Exp168)

00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

- (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)

00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
